---
title: "Maryland Labour Stike Analysis"
author: "Michael V Cumbo"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  word_document: null
  pdf_document:
    latex_engine: xelatex
---

```{r connector, include=FALSE}

library(DBI)
library(RSQLite)

  sql_location <- "~/trade_union-strikes.db"
  driver <- RSQLite::dbDriver("SQLite")
  conn <- RSQLite::dbConnect(driver, sql_location)
db = dbConnect(driver, dbname = sql_location)


```
### Introductions

##### data was updated on **Monday, 7th July 2025**


This report details the strike activity that has taken place in Maryland,and the number of the strikes and the labor unions involved. Thanks to Cornell university and the research team providing the data.

The chart below indicates the number of Labor Strikes that have occurred in region over the past year, it does this by counting the number of strikes associated with a given region. Data is updated on a month to month basis, the current month will not be represented within the data. 

```{r setup,  echo = FALSE, message = FALSE, warning = FALSE }
library(ragg)
library(extrafont)
##install.packages("hrbrthemes")
##library(hrbrthemes)

library(ggplot2)

read_sql <- function(name) {
  driver <- RSQLite::dbDriver("SQLite")
  conn <- DBI::dbConnect(driver, sql_location)
  table <- DBI::dbReadTable(conn,{{name}})
  return(dplyr::as_tibble(table))
  RSQLite::dbDisconnect(conn)
}

sql_list <- function() {
  driver <- RSQLite::dbDriver("SQLite")
  sql_location <- "~/trade_union-strikes.db"
  conn <- RSQLite::dbConnect(driver, sql_location)
  table <- DBI::dbListTables(conn)
  return(table)
  RSQLite::dbDisconnect(conn)
}

execute_sql <- function(statement) {
  sql_location <- "~/trade_union-strikes.db"
  driver <- RSQLite::dbDriver("SQLite")
  conn <- RSQLite::dbConnect(driver, sql_location)
  qw <- RSQLite::dbSendQuery(conn, {{statement}})
  data <- RSQLite::dbFetch(qw)
  return(data)
  RSQLite::dbDisconnect(conn)
}


data <- execute_sql("
            SELECT count(*) AS strikes,
            Year 
            FROM 'Labor-prod' WHERE State LIKE '%Maryland%' 
            GROUP BY Year
            ")
##ggplot(data, aes(x=Year, y=strikes)) +
##  ggplot2::geom_bar()+
##  ggplot2::ggtitle("Strikes in Maryland")


data |>  
  tail(10) |> 
  ggplot( aes(x=Year, y=strikes, label = strikes)) +
   geom_text(hjust=1, vjust=2, check_overlap = FALSE) +
    geom_line( color="grey") +
    geom_point(shape=21, color="black", fill="#69b3a2", size=3) +
    ggplot2::ylim(-2, 30)+
   # hrbrthemes::theme_ipsum() +
    ggtitle("Strikes in Maryland")

```


\pagebreak
#### Strikes from formalized labor unions 

Below is a list of labor organization who have gone on strike within the state, along with their reasons for striking. Please note that there are additional records in the charts not included here, which could be strikes conducted without a formalized labor organization. Data is updated on a month to month basis, the current month will not be represented within the data.



```{sql, connection=db, max.print = 50, echo = FALSE}
SELECT 
"Labor Organization",
"Worker Demands",
 Year
FROM 'Labor-prod'
WHERE State LIKE "%Maryland%" AND "Labor Organization" IS NOT NULL AND NOT "NA"
GROUP BY `Labor Organization`
ORDER BY Year DESC

```

### Charts of Number of Strikes per each year

```{r What does the data Look like nationally, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
strike_month <- function(state, year){
data <- execute_sql(paste0("
            SELECT count(*) AS strikes,
            Year,
            Month
            FROM 'Labor-prod' 
            WHERE State LIKE '%",state,"%' 
            and Year IS ",year,"
            GROUP BY Month
            "))
##ggplot(data, aes(x=Year, y=strikes)) +
##  ggplot2::geom_bar()+
##  ggplot2::ggtitle("Strikes in Maryland")
chart <- data |>  
  tail(10) |> 
  ggplot( aes(x=Month, y=strikes, label = strikes)) +
   geom_text(hjust=1, vjust=2, check_overlap = FALSE) +
    geom_line( color="grey") +
    geom_point(shape=21, color="black", fill="#69b3a2", size=3) +
 ##   ggplot2::ylim(-2, 10)+
##    ggplot2::xlim(1, 12)+
    scale_x_continuous(limits=c(1,12), breaks=seq(1,12,1))+
    scale_y_continuous(limits=c(0,10), breaks=seq(1,10,1))+
#    hrbrthemes::theme_ipsum() +
    ggtitle(paste0("Strikes in ",state," ",year,""))
return(chart)
}


strike_month("Maryland",2021)
strike_month("Maryland",2022)
strike_month("Maryland",2023)
strike_month("Maryland",2024)
strike_month("Maryland",2025)

```

##### Citation 
Kallas, J., Iyer, D. K., & Friedman, E. (2025).
"Labor Action Tracker" Cornell University ILR School & University of Illinois LER School.
  Addison Wesley, Massachusetts,
  2nd Edition,
  1994.