---
title: "Maryland Labour Stike Analysis"
author: "Michael V Cumbo"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---
### Introductions

This report details the strike activity that has taken place in Maryland the last 5 years, the number of the strikes and the labor unions involved. Thanks to Cornell university and the research team providing the data.

```{r setup,  echo = FALSE, message = FALSE, warning = FALSE }
library(extrafont)
library(Cairo)
##install.packages("hrbrthemes")
##library(hrbrthemes)

library(ggplot2)

read_sql <- function(name) {
  driver <- RSQLite::dbDriver("SQLite")
  conn <- DBI::dbConnect(driver, sql_location)
  table <- DBI::dbReadTable(conn,{{name}})
  return(dplyr::as_tibble(table))
  RSQLite::dbDisconnect(conn)
}

sql_list <- function() {
  driver <- RSQLite::dbDriver("SQLite")
  sql_location <- "~/trade_union-strikes.db"
  conn <- RSQLite::dbConnect(driver, sql_location)
  table <- DBI::dbListTables(conn)
  return(table)
  RSQLite::dbDisconnect(conn)
}

execute_sql <- function(statement) {
  sql_location <- "~/trade_union-strikes.db"
  driver <- RSQLite::dbDriver("SQLite")
  conn <- RSQLite::dbConnect(driver, sql_location)
  qw <- RSQLite::dbSendQuery(conn, {{statement}})
  data <- RSQLite::dbFetch(qw)
  return(data)
  RSQLite::dbDisconnect(conn)
}


data <- execute_sql("
            SELECT count(*) AS strikes,
            Year 
            FROM 'Labor-prod' WHERE State LIKE '%Maryland%' 
            GROUP BY Year
            ")
##ggplot(data, aes(x=Year, y=strikes)) +
##  ggplot2::geom_bar()+
##  ggplot2::ggtitle("Strikes in Maryland")


data |>  
  tail(10) |> 
  ggplot( aes(x=Year, y=strikes, label = strikes)) +
   geom_text(hjust=1, vjust=2, check_overlap = FALSE) +
    geom_line( color="grey") +
    geom_point(shape=21, color="black", fill="#69b3a2", size=3) +
    ggplot2::ylim(-2, 30)+
    hrbrthemes::theme_ipsum() +
    ggtitle("Strikes in Maryland")

```


The above charts indicates the number of Labor Strikes that have occurred in Maryland over the pass year, it does this by counting the number of strikes assocated with a given region in this case Maryland. 

\pagebreak
Below is a list of labor organization who have gone on strike within the state.
```{r Who is Going on Strike?, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
data <- execute_sql("
            SELECT 
            `Labor Organization`
            FROM 'Labor-prod' WHERE State LIKE '%Maryland%' 
            GROUP BY `Labor Organization`
            ORDER BY Year
            ")
data |> 
  tibble::as_tibble() |> 
  print.data.frame()


```

## Here are the year to year strike numbers

```{r What does the data Look like nationally, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
strike_month <- function(state, year){
data <- execute_sql(paste0("
            SELECT count(*) AS strikes,
            Year,
            Month
            FROM 'Labor-prod' 
            WHERE State LIKE '%",state,"%' 
            and Year IS ",year,"
            GROUP BY Month
            "))
##ggplot(data, aes(x=Year, y=strikes)) +
##  ggplot2::geom_bar()+
##  ggplot2::ggtitle("Strikes in Maryland")
chart <- data |>  
  tail(10) |> 
  ggplot( aes(x=Month, y=strikes, label = strikes)) +
   geom_text(hjust=1, vjust=2, check_overlap = FALSE) +
    geom_line( color="grey") +
    geom_point(shape=21, color="black", fill="#69b3a2", size=3) +
 ##   ggplot2::ylim(-2, 10)+
##    ggplot2::xlim(1, 12)+
    scale_x_continuous(limits=c(1,12), breaks=seq(1,12,1))+
    scale_y_continuous(limits=c(0,10), breaks=seq(1,10,1))+
    hrbrthemes::theme_ipsum() +
    ggtitle(paste0("Strikes in ",state," ",year,""))
return(chart)
}


strike_month("Maryland",2021)
strike_month("Maryland",2022)
strike_month("Maryland",2023)
strike_month("Maryland",2024)
strike_month("Maryland",2025)

```


