
---
title: "My R Markdown Document"
output:
  html_document:
    theme: cerulean
---


# Introduction


Code chunk connects to a database and generates tables from from the database.

## Loading the database

Here is the code chunk

```{r}
source("~/Lab2/Trade_Union_Global_Analysis/summary_analysis/Enviroment_Setup.R")

suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
})

# connect to the database and pull out the sheet
setwd("~/workbook")
con <- dbConnect(RSQLite::SQLite(), "trade_union_data.db")
dbListTables(con)
february <- as_tibble(dbReadTable(con, "LAT-02.19.24"))
dbDisconnect(con)
```
## prepping the data in table for an analysis

The below chunk edits ZipCode's BargainingUnitSize ApproximateNumberofParticipants to their related data types

```{r}
# Convert Timestamp column to POSIXct format
february$Timestamp <- as.POSIXct(february$Timestamp,
  format = "%m/%d/%Y %H:%M:%S"
)

# mutate zip code to a character
february <- february %>%
  mutate(
    ZipCode = as.character(ZipCode),
    BargainingUnitSize = parse_number(as.character(BargainingUnitSize)),
    ApproximateNumberofParticipants =
      parse_number(as.character(ApproximateNumberofParticipants)),
    Date = format(Timestamp, "%Y-%m-%d"),
    month = format(Timestamp, "%B"),
    Year = format(Timestamp, "%Y"),
    DurationAmount = as.integer(DurationAmount)
  )
```
## check for missing data against the spreedsheet
```{r,echo=FALSE,results='markup'}
# check the number of non NA and NA's in thsi column against the sheet
count_data_busize <- sum(!is.na(february$BargainingUnitSize))
count_na_busize <- sum(is.na(february$BargainingUnitSize))
# exmain the number of notes
count_number_of_notes <- sum(!is.na(february$Notes))

print(paste("the total number of available data points in the BargainingUnitSize vector is", count_data_busize))
print(paste("the total number of missing/blank data points in the BargainingUnitSize vector is", count_na_busize))
print(paste("the total number of missing/blank data points in the notes vector is", count_number_of_notes))
```
## the function to generate bar charts from various state and year vector
```{r}
monthly_plot <- function(state_var, year_var) {
  if (length(year_var) == 1) {
    d <- february %>%
      filter(State == state_var, Year == year_var) %>%
      ggplot(aes(x = month)) +
      geom_bar() +
      labs(title = paste("Number of Strikes in", state_var)) +
      common_theme()
  } else {
    d <- february %>%
      filter(State == state_var, Year %in% year_var) %>%
      ggplot(aes(x = month)) +
      geom_bar() +
      labs(title = paste("Number of Strikes in", state_var, "Per Month")) +
      facet_wrap(~Year, scales = "free_x") +
      common_theme()
  }
  return(d)
}
years <- c("2021", "2022", "2023", "2024")
```

```{r}
monthly_plot("District of Columbia", years)
monthly_plot("Maryland", years)
monthly_plot("Virginia", years)
```
```

