---
title: "Stike Analysis DMV region"
author: "Michael Cumbo"
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```
### Introductions

I was recently reading a copy of "Means and Ends" By Zoe Baker a Anarchist Historian from Lough-brougham University. Zoe is someone I have been following a for a couple of years and was absolutely ecstatic when I found out she was publishing a book on the historical accounts anarchist theory and practice. Her historical accounts of trade unionist are fascinating to me, they managed to capture a picture of history I was never taught in school. Inspired by her writings I wanted to create some visualizations that demonstrate current labor activity in united states. The data from the labor action tracker special thanks to Cornell university and the research team providing the data.

### The Data

The table below shows the District of Columbia, the year, labor organization count, employers and strikes. `labor org count` represent the number of active labor organizations engaging in strike actions. `employers` are the organizations  the labor organization are campaigning against. `strikes` are the number of recorded strikes within a state.   For the year `2024` the data is incomplete, the data is expected to be fully populated by 2025 sometime in January. But for now the data will be populated on a monthly bases. In the future there will be visualization & tables showings months that have activity. For now data tables will be the main way I demonstrate this information.  

```{r dc_data, fig.cap = "Test", echo = FALSE, fig.show="hold", out.width="50%"}
xfun::pkg_load2(c("htmltools", "mime"))
library(targets)
library(knitr)
dc_data <- tar_read(dc_data)
knitr::kable(dc_data, "simple")
md_data <- tar_read(md_data)
knitr::kable(md_data, "simple")
va_data <- tar_read(va_data)
knitr::kable(va_data, "simple")
```
In Figure \@ref(fig:dc_data)
In Figure \@ref(fig:md_data)
In Figure \@ref(fig:va_data)

\newpage

```{r}
national_data <- tar_read(national_data)
knitr::kable(national_data, "simple")
national_strikes <- tar_read(national.monthly.strikes)
knitr::kable(national_strikes,"simple")
```
In Figure \@ref(fig:national_data)
